Gap Puzzles

### 2020-01-05 gap/article/llncs2e/article.tex
Added part 3 of the report, now sleep

\begin{figure}
\includegraphics[width=\textwidth]{images/figure1.png}
\caption{Gap Puzzle example} \label{fig1}
\end{figure}

@@

\section{Approach}

\subsection{Decision Variables}

\subsection{Constraints}

\section{Search Strategy}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/figure1.png}
        \caption{Gap Puzzle example} \label{fig1}
    \end{center}
\end{figure}

@@

\section{Approach}
\paragraph{}
In the specific context of this problem, the constraints used to solve the problem are a translation of the rules of 
the puzzle to Prolog Constraints. The following subsections explain the constraints used in detail.

\subsection{Decision Variables}
To solve this problem we have only a decision variable, the \textit{Points} list. This list stores the coordinates of all
the cells that will be shaded, in the format \textit{[X1,Y1,X2,Y2|...]}. We start by defining that this list will have a 
a length of:

\begin{equation}
    points = 2 * order
\end{equation}

\begin{equation}
    length = 4 * order
\end{equation}

This happens because we can only have two shaded cells in each row. Since the number of rows is equal to the order of our
grid, we a number of points that is two times our order.

\paragraph{}
Then we define the domain of the Decision Variable, this will between zero and the number immediately inferior to our order,
this is because we are considering a system of coordinates starting in zero.

\subsection{Constraints}
\paragraph{}
The first constraint we make is to grant there are only two shaded cells in each row and in each column. We do this 
using the \textbf{restrict\_two(+List,+Order)} predicate. This predicate restricts each number of the domain in the list 
to occur exactly two times in the list. We do this two times, the first for a list containing all the X coordinates of the
solution, and a second time for the Y coordinate. We are able to split this using the \textbf{extractX(+List,-XList)} and
\textbf{extractY(+List,-YList)} predicates. The first one takes a list with the solution format and unifies in 
\textit{XList} all the X coordinates of that list. The \textit{extractY} predicate does the same for Y.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/restrict_two.png}
        \caption{The restrict\_two predicate} \label{fig2}
    \end{center}
\end{figure}

\paragraph{}
Then we restrict the positions of the shaded cells themselves. We do this using the \textbf{restrict\_next(+List)} predicate.
This predicate iterates through the list making sure that no other coordinates in the list are the coordinates of an 
adjacent cell to the any of the other cells and that no two cell coordinates are the same. This predicate calls the
\textbf{restrict\_next\_pair(+List,+X,+Y)} predicate that applies the constraints mentioned above to all the other 
coordinate pairs in the list.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/restrictPair.png}
        \caption{The restrict\_next\_pair predicate} \label{fig3}
    \end{center}
\end{figure}

\section{Search Strategy}
\paragraph{}
So that prolog can search for arbitrary solutions and not different permutations of the same solution, we need to define
a predicate that makes each solution unique. In the present case, this was accomplished by ordering all the points 
of a solution in a crescent order, making each solution unique. This is accomplished by the \textbf{crescent\_order(+List)}
predicate.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/crescent.png}
        \caption{The crescent\_order predicate} \label{fig4}
    \end{center}
\end{figure}
